---
title: "Assignment_1"
output:
  html_document: default
  pdf_document: default
date: "2024-08-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
```

## Data source: https://www.kaggle.com/datasets/danielkyrka/bmw-pricing-challenge/data Importing and reading the data 

```{r}
data<- read_xlsx("C:/Users/echit/Documents/School/Fundamentals of Machine Learning/Assignment_1/bmw_pricing_challenge.xlsx")
```

## Identify a few selected quantitative variables and print descriptive statistics

```{r}
q_variables<-c("mileage","engine_power","price")
summary(data[q_variables])
```

## Identify a few selected categorical variables and print descriptive statistics

```{r}
c_variables<-c("fuel","paint_color","car_type")
table(data[c_variables])
```

## Transform at least one variable. It doesn't matter what the transformation is. Log transformation on the price variable

```{r}
print(data$price)
Log_Price <- log(data$price)
print(Log_Price)
```

## Plot at least one quantitative variable, and one scatterplot - Histogram of the price variable

```{r}
hist(data$price,
main = "Histogram of Price", 
xlab = "Price", 
ylab = "Frequency", 
col = "lightblue", 
border = "black")
```

## Plot at least one quantitative variable, and one scatterplot - Scatterplot of mileage to price

```{r}
plot(data$mileage, data$price, 
     main = "Scatterplot of Mileage vs. Price", 
     xlab = "Mileage", 
     ylab = "Price",
     col = "blue",           # Color of points
     cex = .5)              # Size of points
```